I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-18 Paper/proofs.tex
update proof

				\begin{lemma}\label{lem:subnetwork}
					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$. We call this sub-network $D_I$. In $D_I$, there is no compensating pair.
				\end{lemma}

@@

				Recall the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.

@@

				Notice that $S$ is defined on all nodes $a_i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also). For the domain of $S$, we introduce the following lemma:

>>>>

				\begin{lemma}\label{lem:subnetwork}
					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$. We call this sub-network $D_I$. In $D_I$, there is no compensating pair.
				\end{lemma}

@@

				Recall the sign function of nodes from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, the sign function is no longer total (no longer defined on all nodes).

@@

				Notice that $S$ is defined on all nodes $a_i \in I$. For the domain of $S$, we introduce the following lemma:
